Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-03 cav2017/cav2017.tex
added Order column to the experimental results table
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

We give the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
the name of the respective benchmark, $\mathcal{F}_{\langle I_p,F_p
\rangle}$ is the fixed-point precision used to model the plant, while
\textit{Time} is the total time required to synthesize a \blue{stable} controller
for the given plant, for CEGIS with multi-staged verification as well as
abstraction-based CEGIS.  Timeouts are indicated by~\xmark.  The precision
for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is chosen to be
$I_c = 8$, $F_c = 8$.

@@

\begin{table}
\centering
%\scriptsize
\begin{tabular}{| r | l | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark}  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
1  & Cruise Control      & 8,16   & 8.40\,s & 16,16  &   2.17\,s \\
2  & DC Motor            & 8,16   & 9.45\,s & 20,20  &   2.06\,s \\
3  & Helicopter          & \xmark & \xmark  & 16,16  &   1.37\,s \\
4  & Inverted Pendulum   & 8,16   & 9.65\,s & 16,16  &   0.56\,s \\
5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  &  44.14\,s \\
6  & Magnetic Suspension & 12,20  &10.41\,s & 16,16  &   0.61\,s \\
7  & Pendulum            & 8,16   &14.02\,s & 16,16  &   0.60\,s \\
8  & Suspension          & 12,20  &73.66\,s & \xmark &    \xmark \\
9  & Tape Driver         & 8,16   &10.10\,s & 16,16  &  68.24\,s \\
10 & Satellite           & 8,16   & 9.43\,s & 16,16  &   0.67\,s \\\hline
%
\end{tabular}
\caption{Experimental results\label{tab:results}}
\end{table}

>>>>

We give the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
the name of the respective benchmark, \textit{order} is the number of states, 
$\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used to model the plant, while
\textit{Time} is the total time required to synthesize a \blue{stable} controller
for the given plant, for CEGIS with multi-staged verification as well as
abstraction-based CEGIS.  Timeouts are indicated by~\xmark.  The precision
for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is chosen to be
$I_c = 8$, $F_c = 8$.

@@

\begin{table}
\centering
%\scriptsize
\begin{tabular}{| r | l | c | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
1  & Cruise Control  & 1 & 8,16   & 8.40\,s & 16,16  &   2.17\,s \\
2  & DC Motor          & 2 & 8,16   & 9.45\,s & 20,20  &   2.06\,s \\
3  & Helicopter        & 3 & \xmark & \xmark  & 16,16  &   1.37\,s \\
4  & Inverted Pendulum & 4 & 8,16   & 9.65\,s & 16,16  &   0.56\,s \\
5  & Magnetic Pointer  & 2 & \xmark & \xmark  & 28,28  &  44.14\,s \\
6  & Magnetic Suspension & 2 & 12,20  &10.41\,s & 16,16  &   0.61\,s \\
7  & Pendulum          & 2 & 8,16   &14.02\,s & 16,16  &   0.60\,s \\
8  & Suspension        & 2 & 12,20  &73.66\,s & \xmark &    \xmark \\
9  & Tape Driver       & 3 & 8,16   &10.10\,s & 16,16  &  68.24\,s \\
10 & Satellite          & 2 & 8,16   & 9.43\,s & 16,16  &   0.67\,s \\\hline
%
\end{tabular}
\caption{Experimental results\label{tab:results}}
\end{table}
